TBD

### 2019-02-06 inverse_problems/inverse_problems.tex
no message

If $M_i$ denotes the number of hits at location $i$, $1 \le i \le n$, then by definition of the Poisson process $M_i$'s are iid and $M_i \sim \Poisson(\gamma)$. Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.

With this notation, if $Y \in \R^{n+L}$ is the observed vector, we can write each entry as:
%
\begin{align}
%
Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
%
\end{align}

@@

We will denote by $\M_l$ the moments of $X$:
%
\begin{align}
%
\M_1[i] = \E X[i], \quad 0 \le i \le L-1,
%
\end{align}
%
\begin{align}
%
\M_2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
%
\end{align}
%
and
%
\begin{align}
%
\M_3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
%
\end{align}

We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
%
\begin{align}
%
\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
%
\end{align}
%
\begin{align}
%
\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
%
\end{align}
%
and
%
\begin{align}
%
\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
%
\end{align}

Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.

We will prove the following result:

@@

	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case. The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.

>>>>

If $M_i$ denotes the number of hits at location $i$, $1 \le i \le N-L+1$, then by definition of the Poisson process $M_i$'s are i.i.d.\ and $M_i \sim \Poisson(\gamma)$. Conditional on the value of $M = (M_1,\dots,M_n)$, if we let $X_1^{i},\dots,X_{M_i}^i$ denote the random vectors with position 0 located at $i$, then $X_{k_1}^{i}$ and $X_{k_2}^{i}$ are independent for $k_1 \ne k_2$.
With this notation, we can write each entry as:
%
\begin{align}
%
Y[i] = \sum_{j=0}^{L-1} \sum_{k=1}^{M_{i-j}} X_k^{i-j}[j].
%
\end{align}
\TODO{The well separated model can be also written for a random signal X}

@@

In this section we omit the affect of the noise as it remains the same for the well-separated model.

Let us denote by $m_Y^q$ the moments of $Y$:
%
\begin{align}
%
m_Y^1[i] = \E X[i], \quad 0 \le i \le L-1,
%
\end{align}
%
\begin{align}
%
m_Y^2[i,j] = \E X[i] X[j], \quad 0 \le i,j \le L-1,
%
\end{align}
%
and
%
\begin{align}
%
m_Y^3[i,j,k] = \E X[i] X[j] X[k], \quad 0 \le i,j,k \le L-1.
%
\end{align}

%We will also denote by $\L_l$ the autocorrelations of $X$, $l = 1,2,3$:
%%
%\begin{align}
%%
%\L_1 = \sum_{i=0}^{L-1} \M_1[i] \in \R,
%%
%\end{align}
%%
%\begin{align}
%%
%\L_2(\Delta) = \sum_{i=0}^{L-1} \M_2[i,i+\Delta]  \in \R^L,
%%
%\end{align}
%%
%and
%%
%\begin{align}
%%
%\L_3(\Delta_1,\Delta_2) = \sum_{i=0}^{L-1} \M_3[i,i+\Delta_1,i+\Delta_2]  \in \R^{L \times L}.
%%
%\end{align}
%
%
%Note that in the strongly-separated model, the first three observed moments are, respectively, $\L_1$, $\L_2(\Delta)$, and $\L_3(\Delta_1,\Delta_2)$.
%
%%

In the following,  we show that the moments of the Poisson process can be written in terms of the autocorrelations of the well-separated model.

@@

%	
%	The expected values of the non-zero (for second moment) and off-diagonal (for third moment) terms are the same as without noise, as is true for the strongly-separated case. The same proof of almost sure convergence from my notes for the strongly-separated case also goes through verbatim.
